Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-10 edubots_surveys.Rnw
Reformat and rewrite sentence

Several studies to evaluate chatbots in higher education have been
conducted. For instance, a comprehensive study was presented by Smutny and
Schreiberova \cite{Smutny2020} reviewing 47 educational chatbots implemented in
Facebook Messenger, concluding that most of these chatbots were very basic and
that programmers require of more support to develop and offer tools for
improving coaching methods and students learning. Pérez and collaborators
\cite{perez2020rediscovering} attempted to categorize educational chatbots
attending to their purpose as service-oriented or
teaching-oriented. Service-oriented chatbots include those that provide service
support, such as Ask Holly \cite{meetholly} and Dina \cite{santoso2018dinus},
which respond to students' questions about enrollment and registration. Ask
L. U.  \cite{LancasterUniversity_2019} answers students' frequently asked
questions about schedules, grades, tutors, and societies. LISA
\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate breaking
the ice between new students by introducing them to each other. Ranoliya et
al. \cite{ranoliya2017chatbot} proposed a generic chatbot for university
students that is able to answer frequently asked questions. The University of
Granada deployed Elvira, a chatbot embedded in its main web page
\cite{MOREO20129} to perform the same task. In addition to being able to answer
pre-established frequent questions, it did so from the website of the University
of Granada using an inset persona, voiced by a real person, who lip-synced the
answers. However, in the case of Elvira, the emphasis was on the authenticity of
the speech-mouth and face gestures synchronization rather than making updating
answered questions simpler or more interactive for the administrative staff, or
more open to the rest of the university staff using actual messaging
platforms. In most cases, the embedded search engine was able to provide more
up-to-date and accurate answers than those provided by Elvira, which had to be
updated by hand (and not too often). It was eventually discontinued, and its
technology was not adapted to other platforms, since it did not really provide a
useful service. Its service was not tied to teaching anyway; it was more related
to directory queries and university-wide administrative questions, so even if it
is strictly an example of a chatbot in a university setting, it is not really a
chatbot that can be adopted by teachers to affect the learning outcomes, which
is the focus of this paper.

>>>>

Multiple studies have been conducted to assess the effectiveness of chatbots in
higher education; among them, a comprehensive paper was presented by Smutny and
Schreiberova \cite{Smutny2020} reviewing 47 educational chatbots implemented in
Facebook Messenger, concluding that most of these chatbots were very basic and
that programmers require of more support to develop and offer tools for
improving coaching methods and student learning outcomes. Pérez and
collaborators \cite{perez2020rediscovering} attempted to categorize educational
chatbots attending to their purpose as service-oriented or
teaching-oriented. Service-oriented chatbots include those that provide service
support, such as Ask Holly \cite{meetholly} and Dina \cite{santoso2018dinus},
which respond to students' questions about enrollment and registration. Ask
L. U.  \cite{LancasterUniversity_2019} answers students' frequently asked
questions about schedules, grades, tutors, and societies. LISA
\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate breaking
the ice between new students by introducing them to each other. Ranoliya et
al. \cite{ranoliya2017chatbot} proposed a generic chatbot for university
students that is able to answer frequently asked questions. The University of
Granada deployed Elvira, a chatbot embedded in its main web page
\cite{MOREO20129} to perform the same task. In addition to being able to answer
pre-established frequent questions, it did so from the website of the University
of Granada using an inset persona, voiced by a real person, who lip-synced the
answers. However, in the case of Elvira, the emphasis was on the authenticity of
the speech-mouth and face gestures synchronization rather than making updating
answered questions simpler or more interactive for the administrative staff, or
more open to the rest of the university staff using actual messaging
platforms. In most cases, the embedded search engine was able to provide more
up-to-date and accurate answers than those provided by Elvira, which had to be
updated by hand (and not too often). It was eventually discontinued, and its
technology was not adapted to other platforms, since it did not really provide a
useful service. Its service was not tied to teaching anyway; it was more related
to directory queries and university-wide administrative questions, so even if it
is strictly an example of a chatbot in a university setting, it is not really a
chatbot that can be adopted by teachers to affect the learning outcomes, which
is the focus of this paper.
